---
title: "ANOVA_analysis"
output: html_document
---

# load packages
```{r}
library(tidyverse)
library(stringr)
library(rstatix)
library(ggpubr)
```

# import data
```{r}
dfs <- read.csv("data/new_response_ratios.csv")
```


# create distinct dfs containing the bins based on the different kinds of ratings
```{r}
human <- 
  dfs %>% 
  select(nr,
         age_group, 
         6:9) 


MSE <- 
  dfs %>% 
  select(nr,
         age_group, 
         10:13)



RGB <- 
  dfs %>% 
  select(nr,
         age_group, 
         14:17)


```


# define functions to excecute ANOVE analysis and plot the results
```{r}
ANOV <- function(df) {
  
  colnames(df) <- c("id","age_group","High","Medium","Low","Foil")
  
  df <- gather(df,"bin","new_response_ratio", 3:6)
  
  
  bxp <- ggboxplot(df, 
                 x = "bin", 
                 xlab = "Similarity bin",
                 y = "new_response_ratio", 
                 ylab  = 'Ratio of „new” responses (%)',
                 add = "point")
  
  
  normality <- 
  df %>%
  group_by(bin) %>%
  shapiro_test(new_response_ratio)
  
  
  res.aov <- 
  anova_test(data = df, 
             dv = new_response_ratio, 
             wid = id, 
             within = bin)

  anova_table <- res.aov[[1]]
  mauchly_table <- res.aov[[2]]

  
  bonferroni <- 
    df %>%
    pairwise_t_test(new_response_ratio ~ bin, 
                    paired = TRUE,
                    p.adjust.method = "bonferroni")

  
  
  # Visualization: box plots with p-values
    pwc <- 
      bonferroni %>%
      add_xy_position(x = "bin")
      bxp + 
      stat_pvalue_manual(pwc) +
      labs(
        subtitle = get_test_label(res.aov, detailed = TRUE),
        caption = get_pwc_label(pwc)
      )
  
  df
  print(normality)
  print(anova_table)
  print(mauchly_table)
  print(bonferroni)
  show(pwc)
  
}



# function visualize ANOVA results in a boxplot
ANOV_p <- function(df) {
  
  colnames(df) <- c("id","age_group","High","Medium","Low","Foil")
  
  df <- gather(df,"bin","new_response_ratio", 3:6)
  
  
  bxp <- ggboxplot(df, 
                 x = "bin", 
                 xlab = "Similarity bin",
                 y = "new_response_ratio", 
                 ylab  = 'Ratio of „new” responses (%)',
                 add = "point")
  
  
  normality <- 
  df %>%
  group_by(bin) %>%
  shapiro_test(new_response_ratio)
  
  
  res.aov <- 
  anova_test(data = df, 
             dv = new_response_ratio, 
             wid = id, 
             within = bin)

  anova_table <- get_anova_table(res.aov)
  
  
  
  bonferroni <- 
    df %>%
    pairwise_t_test(new_response_ratio ~ bin, 
                    paired = TRUE,
                    p.adjust.method = "bonferroni")

  
  
  # Visualization: box plots with p-values
    pwc <- 
      bonferroni %>%
      add_xy_position(x = "bin")
      bxp + 
      stat_pvalue_manual(pwc) +
      labs(
        subtitle = get_test_label(res.aov, detailed = TRUE),
        caption = get_pwc_label(pwc)
      )
  
}
```




# compare the ratio of "new" responses in the different similarity bins based on human ratings
```{r}
ANOV(human)
```

```{r}
ANOV_p(human)
```


# compare the ratio of "new" responses in the different similarity bins based on MSE scores
```{r}
ANOV(MSE)
```

```{r}
ANOV_p(MSE)
```




# compare the ratio of "new" responses in the different similarity bins based on RGB comparison scores
```{r}
ANOV(RGB)
```

```{r}
ANOV_p(RGB)
```





# 2 way ANOVA to test whether there is an interaction with age group

```{r}
ANOV2 <- function(x) {
  
  colnames(x) <- c("id","age_group","High","Medium","Low","Foil")
  
  x <- gather(x,"bin","new_response_ratio", 3:6)
  
  x <- convert_as_factor(x, id, age_group, bin)
  x$bin<-factor(x$bin, c("High", "Medium", "Low", "Foil"))


  
#WORKS
model1 <- lm(new_response_ratio ~ bin * age_group, data = x)
Anova(model1,type="III")

res.aov3 <- aov(new_response_ratio ~ bin * age_group, data = x)



summary(res.aov3)


}




ANOV2_plots <- function(x) {
  
  colnames(x) <- c("id","age_group","High","Medium","Low","Foil")
  
  x <- gather(x,"bin","new_response_ratio", 3:6)
  
  x <- convert_as_factor(x, id, age_group, bin)
  x$bin<-factor(x$bin, c("High", "Medium", "Low", "Foil"))


  
#WORKS
model1 <- lm(new_response_ratio ~ bin * age_group, data = x)
Anova(model1,type="III")
plot(model1,2)


res.aov3 <- aov(new_response_ratio ~ bin * age_group, data = x)


  
  bxp <- 
    ggboxplot(x, 
              x = "bin", 
              y = "new_response_ratio",
              color = "age_group", 
              palette = "jco",
              ylab = 'Ratio of "new" responses',
              xlab = "Similarity bin")
  bxp

  
summary(res.aov3)
bxp

}
```


```{r}
ANOV2(human)
```

```{r}
ANOV2_plots(human)
```


```{r}
ANOV2(RGB)
```

```{r}
ANOV2_plots(RGB)
```


```{r}
ANOV2(MSE)
```

```{r}
ANOV2_plots(MSE)
```














