---
title: "APS_data_process"
output: html_document
---
```{r}
library(tidyverse)
library(tibble)

```

```{r}
# read all participants' APS data
APS_list = lapply(list.files(path = "data/APS", pattern="*.csv", full.names = T), 
                   read.csv) 

# read the table containing bin created based on human and computer ratings
bins <- read.csv("data/rating_bins.csv")

```


## functions that will iterate through the list of all partcipants APS data

```{r}
tidy_f <- function(x){
 
  x <- 
    x %>%
    select(TrialType, #Lure / Target / Foil --> Lure + Object Trial
         StimType,
         CurrentImage, #BM
         rec_trial_key.keys,
         EncodingStimType, #EX   ERP / OLP / LLP --> ERP
         EncodingImage) %>%  #EY
     
  # drop location trials, filter for trials that are either foils or
  # what were exact repeats during the encoding phase
  filter(TrialType == "OBJ",
         EncodingStimType == "ERP" | EncodingStimType == "FOIL",
         StimType != "TARGET")
  
  # create new col with img nr
  x$image <- str_sub(x$CurrentImage,18,-6)
  
  
  # create new col with img codes (->>   "a b" , "b a" , a c" ... "b c")
  x$ImgPair <- paste(str_sub(x$CurrentImage, -5,-5),
                    str_sub(x$EncodingImage,-5,-5))
  
  # ->> "ab" , "ac" , "bc" 
  x <- 
    x %>% 
    mutate(abc = ifelse(ImgPair == "a b" | ImgPair == "b a", "ab", 
                        ifelse(ImgPair == "a c" | ImgPair == "c a", "ac",
                           ifelse(ImgPair == "b c" | ImgPair == "c b", "bc",
                                  ImgPair))))
  
  # drop excess cols
  x_tidy <- 
  x %>%
  select(image,
         abc,
         EncodingStimType,
         StimType,
         rec_trial_key.keys) %>% 
    
  mutate(rec_trial_key.keys = ifelse(rec_trial_key.keys == "f", "new", "old"))

  colnames(x_tidy)[5] <- "response"
  
  
  x_tidy
}
```


# attach the different kinds of bins to each trial 
```{r}
tidy_f2 <- function(x){
  
  
  
    # add foils trials 
  foils <- 
    x %>% 
      filter(StimType == "FOIL") 

  # read the csv containing similarity bins based on human ratings, RGB scores & MSE scores
  allratings <- read.csv("data/rating_bins.csv")
  
  # prepare the APS table and the rating_bin table for merge
  allratings$abc <- as.factor(allratings$abc)
  allratings$image <- as.factor(allratings$image)
  arrange(allratings, image)
  x$image <- as.integer(x$image)
  

  x <- merge(x,allratings,by=c("image","abc"))
  

  
  foils$image <- as.integer(foils$image)
  all <- bind_rows(x, foils)
  
  all <- select(all, -X)
  
  # replace NAs with "foil" in the 3 different similarity bin cols
  all[is.na(all)] <- "foil"
  
  all
}
```







```{r}

tidy_f3 <- function(x){
# create a support df that will be binded to the summary table of the response ratios
# it is necessary for adding a "0" if there is not "new" bin in a bin
supp <- data.frame(c("new"), c(0), c(0), c(0))
colnames(supp) <- c("response","n","N","prop")
supp$n <- as.integer(supp$n)
supp$N <- as.integer(supp$N)

# create an empty vector to which the ratio of "new" responses will be appended
# of each bin type (foil,high,medium,low) of each comparison method (human, RGB, MSE)
vec <- numeric(0)



# calculating the ratio of "new" responses in each scenario 

###human ratings
temp <- 
  x %>% 
  filter(average_human_rating == "high") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(average_human_rating == "medium") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(average_human_rating == "low") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(average_human_rating == "foil") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

###MSE ratings
temp <- 
  x %>% 
  filter(MSE == "high") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(MSE == "medium") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(MSE == "low") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(MSE == "foil") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])
  

###RGB ratings
temp <- 
  x %>% 
  filter(RGB == "high") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(RGB == "medium") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(RGB == "low") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])

#
temp <- 
  x %>% 
  filter(RGB == "foil") %>% 
  group_by(response) %>% 
  summarise(n = n()) %>% 
  mutate(N = sum(n),
            prop = round(n/N*100)) %>% 
  filter(response == "new") %>% 
  rbind(supp)

vec <- append(vec, temp$prop[[1]])




new_response_ratios <<- rbind(new_response_ratios, vec)
colnames(new_response_ratios) <<- c("human_H", "human_M", "human_L", "human_F",
                                   "MSE_H", "MSE_M", "MSE_L", "MSE_F",
                                   "RGB_H", "RGB_M", "RGB_L", "RGB_F")


}
```







```{r}

# create an empty df to which each participants "new" response ratios
# will be added row by row (by the tidy_f3 function)
new_response_ratios <- data.frame(matrix(ncol = 12, nrow = 0))
colnames(new_response_ratios) <- c("human_H", "human_M", "human_L", "human_F",
                                   "MSE_H", "MSE_M", "MSE_L", "MSE_F",
                                   "RGB_H", "RGB_M", "RGB_L", "RGB_F")

```


# apply functions to each APS df 
# -> fill the rows of new_response_ratios table with participants' "new" response ratios in different bins 
```{r}
APS_list <- map(APS_list, tidy_f)
APS_list <- map(APS_list, tidy_f2)
APS_list <- map(APS_list, tidy_f3)
```



# add participant nr & age to the df
```{r}
nr <- 1:17
age_group <- c("OA","OA","OA","OA",
               "YA","YA","YA","YA",
               "YA","YA","YA","YA",
               "YA","YA","YA","YA",
               "YA")
age <- c(NA, NA, NA, NA,
         23,21,23,21,23,22,24,20,41,23,20,24,19)

sex <- c(NA, NA, NA, NA,
         "female","female","female","female","female",
         "female","male","female","male",
         "female","female","female","female")


new_response_ratios <- add_column(new_response_ratios, nr, .before = "human_H")

new_response_ratios <- add_column(new_response_ratios, age_group, .before = "human_H")

new_response_ratios <- add_column(new_response_ratios, age, .before = "human_H")

new_response_ratios <- add_column(new_response_ratios, sex, .before = "human_H")

```


# exclude participant 6 beacuse their ratio of "new" responses in all foil bins was 0
```{r}
new_response_ratios = new_response_ratios[-6,]
```

# export data 
```{r}
write.csv(new_response_ratios, "data/new_response_ratios.csv")
```


