---
title: "ICC_calc.rmd"
output: html_document
---

```{r}
library(tidyverse)
library(reticulate)
library(psych)
```

```{r}
processed <- read.csv("all_ratings.csv")
processed <- select(processed, -X)

# calculate mean human rating score for each image pair
processed$human_ratings <- (processed$YA_average_ratings + processed$OA_average_ratings) / 2

raw_ratings <- read.csv("individual_ratings_for_ICC.csv")
```



Generally speaking, the ICC determines the reliability of ratings by comparing the variability of different ratings of the same individuals to the total variation across all ratings and all individuals.

A high ICC (close to 1) indicates high similarity between values from the same group.
A low ICC (ICC close to zero) means that values from the same group are not similar

Due to the large number of pairs, we cannot let each rater rate all pairs. Therefore, our experimental design suits ICC(1,k): each pair is rated by a different set of randomly selected raters, and the result is based on the average of these k raters.

## # #report# # ##
The intra-class correlation coefficient was computed to assess the agreement between three doctors in rating the anxiety levels in 20 individuals. There was a poor absolute agreement between the three doctors, using the two-way random effect models and “single rater” unit, kappa = 0.2, p = 0.056.
## # # # # # # ##

```{r}
# ICC Yab
raw_ratings %>% 
select(ya1.1,ya1.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```

```{r}
# ICC Yac
raw_ratings %>% 
select(ya2.1,ya2.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```


```{r}
# ICC Ybc
raw_ratings %>% 
select(ya3.1,ya3.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```

```{r}
# ICC Oab
raw_ratings %>% 
select(oa1.1,oa1.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```

```{r}
# ICC Oac
raw_ratings %>% 
select(oa2.1,oa2.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```


```{r}
# ICC Obc
raw_ratings %>% 
select(oa3.1,oa3.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```

```{r}
# ICC YOab
raw_ratings %>% 
select(ya1.1,ya1.2,oa1.1,oa1.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```
```{r}
# ICC YOac
raw_ratings %>% 
select(ya2.1,ya2.2,oa2.1,oa2.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```
```{r}
# ICC YOcb
raw_ratings %>% 
select(ya3.1,ya3.2,oa3.1,oa3.2) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()
```

```{r}
head(processed)
```


```{r}
#ICC human raters and pixel based scores
processed %>% 
select(RGB, human_ratings) %>% 
filter(.[1] != -1,
       .[2] != -1) %>% 
ICC()

```


```{r}
#correlate human & pixel based ratings
cor(as.numeric(processed$human_ratings), as.numeric(processed$RGB), method = "pearson")

shapiro_test(processed, human_ratings)

hist(processed$human_ratings)

res2 <- cor.test(processed$RGB, processed$MSE,  method = "spearman")
res2
```

