---
title: "human_similarity_ratings"
output: html_document
---

# Load packages
```{r}
library(tidyverse)
library(reticulate)
library(psych)
```

# Read YA data
```{r}
ya1.1 <- read.table("data/human_ratings/1.1.txt")
ya1.2 <- read.table("data/human_ratings/1.2.txt")

ya2.1 <- read.table("data/human_ratings/2.1.txt")
ya2.2 <- read.table("data/human_ratings/2.2.txt")

ya3.1 <- read.table("data/human_ratings/3.1.txt")
ya3.2 <- read.table("data/human_ratings/3.2.txt")
```


# Read OA data
```{r}
oa1.1 <- read.table("data/human_ratings/1.1_o.txt")
oa1.2 <- read.table("data/human_ratings/1.2_o.txt")

oa2.1 <- read.table("data/human_ratings/2.1_o.txt")
oa2.2 <- read.table("data/human_ratings/2.2_o.txt")

oa3.1 <- read.table("data/human_ratings/3.1_o.txt")
oa3.2 <- read.table("data/human_ratings/3.2_o.txt")
```


# create a list containing all YAs' data
```{r}
ya_data <- list(ya1.1, ya1.2, ya2.1, ya2.2, ya3.1, ya3.2)
names(ya_data) <- c("ya1.1", "ya1.2","ya2.1", "ya2.2", "ya3.1", "ya3.2")
```


# create a list containing all OAs' data
```{r}
oa_data <- list(oa1.1, oa1.2, oa2.1, oa2.2, oa3.1, oa3.2)
names(oa_data) <- c("oa1.1", "oa1.2","oa2.1", "oa2.2", "oa3.1", "oa3.2")
```


# define a function that arranges the data
```{r}
tidy_f <- function(x) {
x <- data.frame(x)

colnames(x) <- c("image","group","rating","RT","same")

# remove practice trials: 1st 20 rows
x <- slice(x, -(1:20))

# remove the trials with the same images 
x <- filter(x, same == 0)

x <- arrange(x, image)
x
}
```


# tidy all participants' data
```{r}
ya_data <- map(ya_data, tidy_f)

oa_data <- map(oa_data, tidy_f)
```




# create a df containing each participant's rating scores
```{r}
individual_ratings <- data.frame(c(1:181),
                              ya_data$ya1.1[3],
                              ya_data$ya1.2[3],
                              ya_data$ya2.1[3], 
                              ya_data$ya2.2[3],
                              ya_data$ya3.1[3], 
                              ya_data$ya3.2[3],
                              
                              oa_data$oa1.1[3],
                              oa_data$oa1.2[3],
                              oa_data$oa2.1[3], 
                              oa_data$oa2.2[3],
                              oa_data$oa3.1[3], 
                              oa_data$oa3.2[3])

colnames(individual_ratings) <- c("image",
                               "ya1.1",
                              "ya1.2",
                              "ya2.1", 
                              "ya2.2",
                              "ya3.1", 
                              "ya3.2",
                              
                              "oa1.1",
                              "oa1.2",
                              "oa2.1", 
                              "oa2.2",
                              "oa3.1", 
                              "oa3.2")


write.csv(individual_ratings, "individual_ratings_for_ICC.csv")
```



# calculate the average of ratings of each image pair
```{r}
average_ratings <- 
  individ_ratings %>% 
  mutate(ya1.mean = ifelse(ya1.1 == -1, ya1.2, 
                        ifelse(ya1.2 == -1, ya1.1, 
                               (ya1.1+ya1.2)/2))) %>% 
  
  mutate(ya2.mean = ifelse(ya2.1 == -1, ya2.2, 
                        ifelse(ya2.2 == -1, ya2.1, 
                               (ya2.1+ya2.2)/2))) %>% 
  
  mutate(ya3.mean= ifelse(ya3.1 == -1, ya3.2, 
                        ifelse(ya3.2 == -1, ya3.1, 
                               (ya1.1+ya3.2)/2))) %>% 


  mutate(oa1.mean = ifelse(oa1.1 == -1, oa1.2, 
                        ifelse(oa1.2 == -1, oa1.1, 
                               (oa1.1+oa1.2)/2))) %>% 
  
  mutate(oa2.mean = ifelse(oa2.1 == -1, oa2.2, 
                        ifelse(oa2.2 == -1, oa2.1, 
                               (oa2.1+oa2.2)/2))) %>% 
  
  mutate(oa3.mean = ifelse(oa3.1 == -1, oa3.2, 
                        ifelse(oa3.2 == -1, oa3.1, 
                               (oa1.1+oa3.2)/2)))


```




# histograms of the rating distributions
```{r}
ggplot(average_ratings, aes(factor(ya1.mean))) +
  geom_bar()

ggsave("ya_group1_mean_ratings.png")

ggplot(average_ratings, aes(factor(ya2.mean))) +
  geom_bar()

ggsave("ya_group2_mean_ratings.png")

ggplot(average_ratings, aes(factor(ya3.mean))) +
  geom_bar()

ggsave("ya_group3_mean_ratings.png")


ggplot(average_ratings, aes(factor(oa1.mean))) +
  geom_bar()

ggsave("oa_group1_mean_ratings.png")

ggplot(average_ratings, aes(factor(oa2.mean))) +
  geom_bar()

ggsave("oa_group2_mean_ratings.png")

ggplot(average_ratings, aes(factor(oa3.mean))) +
  geom_bar()

ggsave("oa_group3_mean_ratings.png")

```

# calculate the average of the ratings of OAs and YAs
```{r}
average_ratings <- 
  average_ratings %>% 
  mutate(group1.mean = (ya1.mean+oa1.mean)/2,
         group2.mean = (ya2.mean+oa2.mean)/2,
         group3.mean = (ya3.mean+oa3.mean)/2)
```


# creating lure bins for ab ac and bc image pairs

```{r}
rating_bins <- 
  average_ratings %>% 
  mutate(ab = cut(group1.mean,3,labels = c("low","medium","high"))) %>% 
 
  mutate(ac = cut(group2.mean,3,labels = c("low","medium","high"))) %>% 
  
  mutate(bc = cut(group3.mean,3,labels = c("low","medium","high"))) 



```


# create a tidy df with similarity bins based on all human ratings
```{r}
rating_bins <- 
  rating_bins %>% 
  select(image, ab, ac, bc) %>% 
  gather("abc","average_human_rating",ab:bc) %>% 
  arrange(image)
```

# compare human ratings with pixel wise correlation

1. read RGB_difference_score data
2. read MSE data

3. create a df with the following cols: 
  - image number, human rating bins
  
4. create a 3rd col with the matching RGB values
5. create a 4th col with the matching MSE values

6. correlate the 2nd col with the 3rd and 4th

```{r}
RGB <- read.csv("data/RGB_diff_matrix.csv", row.names = 1, header= TRUE)

MSE <- read.csv("data/MSE_matrix.csv",row.names = 1, header= TRUE)

```

```{r}

# create a vector with the RGB comparison scores 
# in the seq: 1a-1b, 1a-1c, 1b-1c, 2a-2b, ... , 181c-181b


RGB_values = list()
j = -1

for (i in 1:181) {
    
    j = j + 1

    RGB_values[j*3 + 1] = RGB[[i*2 + j]][[j*3+1]]
    RGB_values[j*3 + 2] = RGB[[i*3]][[j*3+1]]
    RGB_values[j*3 + 3] = RGB[[i*3]][[i*2 + j]]
}

RGB_values <- unlist(RGB_values)
RGB_values <- as.factor(RGB_values)
```

# create similarity bins based on the RGB scores
```{r}
rating_bins$RGB_scores <- as.factor(RGB_values)
rating_bins$RGB <- cut(as.numeric(rating_bins$RGB_scores),3,labels = c("low","medium","high"))
```

```{r}
# create a vector with the MSE comparison scores 
# in the seq: 1a-1b, 1a-1c, 1b-1c, 2a-2b, ... , 181c-181b


MSE_values = list()
j = -1

for (i in 1:181) {
    
    j = j + 1

    MSE_values[j*3 + 1] = MSE[[i*2 + j]][[j*3+1]]
    MSE_values[j*3 + 2] = MSE[[i*3]][[j*3+1]]
    MSE_values[j*3 + 3] = MSE[[i*3]][[i*2 + j]]
}

MSE_values <- unlist(MSE_values)
MSE_values <- as.factor(MSE_values)
```

# create similarity bins based on the MSE scores
```{r}
rating_bins$MSE_scores  <- as.factor(MSE_values)
rating_bins$MSE <- cut(as.numeric(rating_bins$MSE_scores),3,labels = c("low","medium","high"))
```

```{r}
rating_bins <- select(rating_bins, -RGB_scores, -MSE_scores)
```



```{r}
write.csv(rating_bins, "data/rating_bins.csv")
```



















```{r}
# define a function that finds the vals from the EGB matrix

find_value <- function(matrix, image_nr) {
  
  ab = matrix[[image_nr*2 + (image_nr-1)]][[(image_nr-1)*3+1]]
  ac = matrix[[image_nr*3]][[(image_nr-1)*3+1]]
  bc = matrix[[image_nr*3]][[image_nr*2 + (image_nr-1)]]
  
  c(ab,ac,bc) 
  
}



find_value2 <- function(im1, im2) {
  
  a = RGB[[im1]][[im2]]
  
  a 
  
}
```

```{r}
find_value(RGB,100)[3]
```
```{r}
#find_value2('100a','X100a')
RGB['X100a']


cor(RGB['X3a'],MSE['X3a'])
```

```{r}
j = 1
i = 2


a1 = i*2 + j
a2 = j*3 + 1

b1 = i*3
b2 = j*3 + 1

c1 = i*3
c2 = i*2 + j

print(a1)
print(a2)
print(b1)
print(b2)
print(c1)
print(c2)
```


define a function that finds the vals from the EGB matrix

find_value <- function(image_nr, first_letter, second_letter)


```{r}
write.csv(ratings, "data/ratings.csv")
```


  